Analysis on The COVID-19 Pandemic Disrupted Both School Bullying and Cyberbullying

### 2023-02-21 Outputs/Paper/paper.qmd
update paper

As discussed earlier, there has been a significant increase in anti-Asian culture in the United States over the past year. Many may be attributed to the spread of misinformation and xenophobic rhetoric related to the COVID-19 pandemic, which has stoked hatred against Asian communities. Reports show that 81% of Asian adults state violence against them is increasing. Over 3800 hate-related verbal and physical assaults against Asian Americans have been reported during the pandemic.

@@

If my paper were 10 pages, then should be be at least 2.5 pages. The discussion is a chance to show off what you know and what you learnt from all this.

@@

## Comparing top 10 with highest Asian population and bottom 10 states with lowest Asian population

>>>>

@@

write a little here

@@

## Comparing top 10 with highest Asian population and bottom 10 states with lowest Asian population
write a little here
